%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

\documentclass[]{awesome-cv}
\usepackage{textcomp}
\fontdir[fonts/]
\newcommand*{\sectiondir}{resume/}

\colorlet{awesome}{awesome-darknight}

\begin{document}
    
\begin{center}
	\headerfirstnamestyle{João} \headerlastnamestyle{Carrasco} \\
	\vspace{2mm}
	{\faEnvelope\ carrascojp@outlook.com} | {\faMobile\ +1 647 338 8943} | {\faMapMarker\ Toronto, Ontario, CA} \\ 
	{\faLinkedinSquare\ \color{darkblue}{https://www.linkedin.com/in/joao-carrasco/}} | {\faGithub\ \color{darkblue}{https://github.com/jpcrs/}} 
\end{center}

\cvsection{About me}
\begin{txtx}
As a developer, I prioritize simple solutions over over-engineered ones. I have experience working on diverse projects in various industries, including Telecom, Banking, IoT, and Networking, with a focus on backend engineering. In addition to my professional work, programming is also a hobby of mine, and I enjoy exploring new technologies and messing with reverse engineering. Beyond programming, I spend my time reading, learning music, playing, and spending time with friends.
\end{txtx}

\cvsection{Work Experience}
\begin{cventries}
	\cventry
	{Senior Software Engineer}
	{Akamai Technologies (Previously Asavie, acquired Oct 2020)}
	{Dublin, IE}
	{Jun 2018 – Aug 2022}
	{\begin{cvitems}
		\item {Designed, provisioned, built, and maintained highly scalable APIs for Akamai IoT security services using modern \textbf{.NET Core microservices} running on \textbf{Docker/Kubernetes (AKS)} and \textbf{Azure Functions}, implementing patterns like \textbf{CQRS}, \textbf{Event Sourcing}, and \textbf{Actor Model} concepts. Using mostly \textbf{Azure and Azure DevOps for CI/CD}.}
		\item {Led design sessions for system architecture, \textbf{OpenAPI} design, and new feature implementation details.}
		\item {Automated cloud resource creation and management using \textbf{Pulumi (C\# and TypeScript)} and \textbf{Terraform}.}
		\item {Built and maintained pipelines for automated build/test/deployment of applications using \textbf{Azure DevOps}, with automated deployment to \textbf{Kubernetes}, \textbf{Azure Functions}, and \textbf{WebApps} across multiple environments.}
		\item {Integrated our systems with centralized solutions for logs, traces, and metrics like \textbf{Jaeger}, \textbf{ELK}, and \textbf{Grafana}.}
		\item {Mentored new team members joining the team.}
		\item \textit{Technology Stack: ASP.NET Core, Docker, Kubernetes, Pulumi/Terraform, CosmosDB, Azure Functions, Azure Storage Queue, Azure Event Grid, Azure Service Bus, Azure Event Hubs, and more.}
		\end{cvitems}}
	\cventry
	{Software Engineer}
	{Itaú}
	{São Paulo, BR}
	{Jun 2017 – Apr 2018}
	{\begin{cvitems}
		\item {Developed and maintained \href{https://play.google.com/store/apps/details?id=com.itau}{\color{darkblue}{Banco Itaú}}, \href{https://play.google.com/store/apps/details?id=com.itaucard.activity}{\color{darkblue}{ItaúCard}} and \href{https://play.google.com/store/apps/details?id=com.itau.iti}{\color{darkblue}{ITI}} apps, worked mostly with \textbf{Android} but sometimes also with \textbf{iOS}, and developed API\textquotesingle{}s with \textbf{Node.js}. Had some experiences with CI/CD (\textbf{Jenkins} and \textbf{SonarQube}).}
		\item \textit{Technology stack: Node.js, Express, Android (EventBus, Retrofit, RxJava), iOS (Objective-C and Swift).}
		\end{cvitems}}
	\cventry
	{Full Stack Engineer}
	{MUTANT BR}
	{São Paulo, BR}
	{Apr 2017 – Jul 2017}
	{\begin{cvitems}
		\item {Developed web systems for NET and Claro, using mainly Microsoft technology stack, \textbf{Agile (Scrum)}, TFS for versioning and \textbf{SQLServer} for database. Also responsible for creating some CI jobs using \textbf{Jenkins} and \textbf{Octopus Deploy}.}
		\end{cvitems}}
	\cventry
	{Full Stack Engineer}
	{TOTVS juriTIs}
	{São Paulo, BR}
	{Jul 2015 – Jan 2017}
	{\begin{cvitems}
		\item {Developed web systems for some of the biggest legal offices in Brazil, using mainly Microsoft technology stack, Agile (Scrum), databases with TSQL (SQLServer) and PL/SQL and Crystal Reports for reports.}
		\item \textit{Technology stack: ASP.NET MVC5, EF5, WebAPI v2, OData v2, LINQ, SignalR, HangFire, AutoMapper, SimpleInjector, Durandal, KnockoutJS, BreezeJS, JQuery, KendoUI.}
		\end{cvitems}}
	\cventry
	{Teacher Assistant}
	{Instituto Federal de Educação, Ciência e Tecnologia de São Paulo}
	{São Paulo, BR}
	{May 2013 – Mar 2014}
	{\begin{cvitems}
		\item Paid internship during college, responsible for helping in Programming Logic and C Development classes.
		\end{cvitems}}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming Languages: {\skill{ C\#, JavaScript, TypeScript }} \\
		Technologies: {\skill{ Azure, Docker, Kubernetes, ELK, Pulumi, Terraform, SQL (MS SQLServer, Postgre), No-SQL (CosmosDB, MongoDB) }} \\
		Used Previously: {\skill{Clojure, Go, Java, Python}} \\
		Studying: {\skill{ Rust, F\# }} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-9mm}
\cvsection{Education}
\begin{cventries}
	\cventry
	{Bachelor in Technology}
	{Instituto Federal de Educação, Ciência e Tecnologia de São Paulo}
	{São Paulo, SP}
	{2012 – 2016}
	{}
\end{cventries}
\end{document}